Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-05-20 doc/manuscript/translocation.qmd
Minor edits to Results

To determine whether MYL frog populations show an evolutionary response to Bd, we compared frog genomes between populations with contrasting histories of Bd exposure.
Specifically, we compared frog genomes sampled in four populations that have not yet experienced a Bd-caused epizootic ("naive") [@zhou2015] versus in five populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering"; @fig-allelefrequencies) [@knapp2016; @vredenburg2010].
These recovering populations exist in an enzootic state [@briggs2010], characterized by high Bd prevalence and, in adults, moderate Bd infection intensity ("load") that is typically well below the level expected to cause mortality [@vredenburg2010].
(See SI Appendix for additional details regarding the study design.)

@@

Estimates of frog survival during the 1-year period following translocation indicate that survival was highly variable between recipient sites, but relatively constant within recipient sites (for the subset of sites that received multiple translocations; @fig-translocation-survival).
As such, the average survival of frogs in the first translocation to a site was an important predictor of survival of frogs in subsequent translocations to that site (@fig-transsurvival-postdens).
This suggests an important effect of site characteristics and/or (site \* frog) interactions on frog survival.
In addition, 1-year survival was higher for frogs translocated later in the study period than earlier (@tbl-survival-earlylate), which we suggest resulted primarily from our improved ability to choose recipient sites with higher habitat quality for *R. sierrae*.
Finally, Bd loads were fairly consistent before versus after translocation and loads were nearly always well below the level indicative of severe chytridiomycosis and associated frog mortality (@fig-bdload-beforeafter) [@joseph2018; @vredenburg2010].
Additional details on methods used to estimate Bd loads are provided in the SI Appendix.

>>>>

To determine whether MYL frog populations show an evolutionary response to Bd, we compared frog genomes between populations with contrasting histories of Bd exposure.
Specifically, we compared frog genomes sampled in 4 populations that have not yet experienced a Bd-caused epizootic ("naive") [@zhou2015] versus in 5 populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering"; @fig-allelefrequencies) [@knapp2016; @vredenburg2010].
These recovering populations exist in an enzootic state [@briggs2010], characterized by high Bd prevalence and, in adults, moderate Bd infection intensity ("load") that is typically well below the level expected to cause mortality [@vredenburg2010].
(See SI Appendix for additional details regarding the study design.)

@@

Estimates of frog survival during the 1-year period following translocation indicate that survival was highly variable between recipient sites, but relatively constant within recipient sites (for the subset of sites that received multiple translocations; @fig-translocation-survival).
As such, the average survival of frogs in the first translocation to a site was an important predictor of survival of frogs in subsequent translocations to that site (@fig-transsurvival-postdens).
This suggests an important effect of site characteristics and/or (site \* frog) interactions on frog survival.
In addition, 1-year survival was higher for frogs translocated later in the study period than earlier (@tbl-survival-earlylate), which we suggest resulted primarily from our improved ability to choose recipient sites with higher habitat quality for *R. sierrae*.
Finally, Bd loads were fairly consistent before versus after translocation and loads were nearly always well below the level indicative of severe chytridiomycosis and associated frog mortality (@fig-bdload-beforeafter) [@joseph2018; @vredenburg2010].
